---
title: "Code for the paper 'A Multivariate Longitudinal Functional Model for Repeatedly-Observed Human-Movement Data'"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

![](outputs/figures/mocap-pic.pdf)

## Repository Structure:  

--- 
* :open_file_folder: **code**
  * :open_file_folder: **analysis** -- scripts used to perform the data analysis.
    * :page_facing_up: [01 - Create Plot for Introduction](code/analysis/01-introduction-plot.R)
    * :page_facing_up: [02 - Create Plot of Stride Timings](code/analysis/02-strides-timing-plot.R)
    * :page_facing_up: [03 - Prepare Data for Analysis](code/analysis/03-data-preparation.R) ([extra figures](code/analysis/03-data-preparation-extra-plot.R))
    * :page_facing_up: [04 - Split Data into Test and Training Samples](code/analysis/04-test-train-split.R)
    * :page_facing_up: [05 - mv-FPCA basis Representation](code/analysis/05-basis-representation.R)
    * :page_facing_up: [06 - Linear Mixed Models of mv-FPCA Scores](code/analysis/06-scores-modelling.R) ([extra figures](code/analysis/06))
    * :page_facing_up: 07 - Individual Random Effects Analysis ([Script 1](code/analysis/07-individual-fitted-mv-FPC1.R), [Script 2](code/analysis/07-individual-analysis-predictions.R), [Script 3](code/analysis/07-individual-analysis-test-error.R), [Script 4](code/analysis/07-individual-analysis-changes.R))
    * :page_facing_up: 08 - Fixed Effects Analysis ([Script 1](code/analysis/08-fixef-results-post-processing.R), [Script 2](code/analysis/08-fixef-spline-coef.R))
  * :open_file_folder: **functions** -- custom functions for modelling data analysis.
    * :page_facing_up: [Centering a (multivariate) object around a different mean](code/functions/center_fd_around_new_mean.R)
    * :page_facing_up: [Decentering a (multivariate) object around a different mean](code/functions/decenter_fd_around_new_mean.R)
    * :page_facing_up: [Helper functions for manipulating `fd` objects](code/functions/functions-helper-smoothing.R)
    * :page_facing_up: [Project (multivariate) functional data (`fd` object) onto (multivariate) FPCs (`pca.fd` object)](code/functions/project_data_onto_fpcs.R)  
    * :page_facing_up: [Computing the (%) of Variance Explained by a mv-FPCA reconstruction](code/functions/variance_explained_reconstruction.R)
    * :page_facing_up: [Custom theme for figures](code/functions/theme_gunning.R)
    * :page_facing_up: [Functions to generate data from a multilevel longitudinal design for the simulation](code/functions/generate_design.R)
    * :page_facing_up: [Generate data from a polynomial scalar longitudinal model for the simulation](code/functions/generate_polynomial_model_basis_coefficient.R)
    * :page_facing_up: [Generate multiple basis coefficients (i.e., mv-FPC scores) from a polynomial scalar longitudinal model for the simulation](code/functions/generate-basis-coefficient-matrix.R)
    * :page_facing_up: [Construct an `fd` object by combining pca.fd object and matrix of PCA scores](code/functions/construct_fd_from_scores.R)
     * :page_facing_up: [Generate smooth Gaussian noise to add to simulated functional data](code/functions/function-generate-smooth-noise.R)
     * :page_facing_up: [Modified version of `pca.fd()` to choose $K$ based on proportion of variance explained.](code/functions/pca.fd_pve_cutoff.R)
     * :page_facing_up: [Wrapper function to extract FPCA scores from a `pca.fd()` object and add them to a data frame.](code/functions/add_pca.fd_scores_to_df.R)
     * :page_facing_up: [Function to fit a polynomial scalar longitudinal model the to mv-FPC scores.](code/functions/fit_poly.R)
     * :page_facing_up: [Function to fit a "naive" model the to mv-FPC scores.](code/functions/fit_naive_spline_intercept.R)
     * :page_facing_up: [Function to fit a ml-FPCA model the to mv-FPC scores.](code/functions/fit_fpca.R)
     * :page_facing_up: [Function to fit a natural spline model the to mv-FPC scores.](code/functions/fit_spline.R)
     * :page_facing_up: [Reduced version of the above model.](code/functions/fit_spline_subject_ri_side.R)
     * :page_facing_up: [Function to calculate average integrated squared prediction error for functional observations.](code/functions/calculate_prediction_error.R)
     * :page_facing_up: [Function to calculate individual integrated squared prediction errors for functional observations.](code/functions/calculate_individual_prediction_errors.R)
     * :page_facing_up: [Convenience function to split data into train and test in simulation.](code/functions/split_train_test.R)
     * :page_facing_up: [Convenience function to load all functions needed in the simulation.](code/functions/source_all_simulation_functions.R)
     * :page_facing_up: [Convenience function to add polynomial terms to a data frame.](code/functions/add_poly_to_df.R)
     * :page_facing_up: [Convenience function to add natural spline terms to a data frame.](code/functions/add_natural_splines_to_df.R)
     * :page_facing_up: [Function to extract fixed-effects coefficients from a list of fitted `lmerMod` objects.](code/functions/extract_fixef_coef.R) 
     * :page_facing_up: [Conveninence function to load all functions for data analysis.](code/functions/source_all_analysis_functions.R)
     * :page_facing_up: [Conveninence functions for post processing results.](code/functions/post-processing-functions.R)
     * :page_facing_up: [Function to calculate rate of change in longitudinal direction](code/functions/calculate_rate_of_change.R)
     * :page_facing_up: [Function to do bootstrap of subjects](code/functions/bootstrap_of_subjects.R)
     
  * :open_file_folder: **tests** -- some basic tests for the custom functions.
      * :page_facing_up: [Test for `center_fd_around_new_mean()`](code/functions/tests/test-center_fd_around_new_mean.R)
      * :page_facing_up: [Test for `decenter_fd_around_new_mean()`](code/functions/tests/test-decenter_fd_around_new_mean.R)
      * :page_facing_up: [Test for `variance_explained_reconstruction()`](code/functions/tests/test-variance-explained-reconstruction.R)
      * :page_facing_up: [Test for `generate_design_multiple_subjects()`](code/functions/tests/test-generate-design.R)
       * :page_facing_up: [Test for `generate_polynomial_model_basis_coefficient()`](code/functions/tests/test-generate_polynomial_model_basis_coefficient.R)
       * :page_facing_up: [Test 1 for `generate_basis_coefficient_matrix()`](code/functions/tests/test-generate-basis-coefficient-matrix-01.R)
       * :page_facing_up: [Test 2 for `generate_basis_coefficient_matrix()`](code/functions/tests/test-generate-basis-coefficient-matrix-02.R)
       * :page_facing_up: [Test for `construct_fd_from_scores()`](code/functions/tests/test_construct_fd_from_scores.R)
       * :page_facing_up: [Tests for `calculate_rate_of_change()`](code/functions/tests/test_calculate_rate_of_change.R)
       * :page_facing_up: [Tests for `calculate_individual_prediction_errors()`](code/functions/tests/test_calculate_individual_prediction_errors.R)
       * :page_facing_up: [Tests for `bootstrap_of_subjects()`](code/functions/tests/test_bootstrap_of_subjects.pdf)
* :open_file_folder: **outputs**
   * :open_file_folder: **tables** -- tables containing data-analysis results. Some are stored as `.csv` files while others have been exported to $TeX$ using `{xtable}` for inclusion in the paper.
   * :open_file_folder: **figures** -- figures for the manuscript, all created in $TeX$ using `{tikzDevice}` and linked to overleaf, where the file [figures.tex](outputs/figures/figures.tex) compiles all the individual $TeX$ files.
   * 💾 also contains `.rds` objects saved at various stages of the data analysis
* :open_file_folder: **data** -- contains the main dataset used in analysis and small data sets used to create the introduction and stride-timing plots.

## Reproducibility

`sessionInfo()` from the model fit:

```{r, echo = FALSE}
model_fit_results <- readRDS(here::here("outputs", "model-fit-results.rds"))
model_fit_results$session_info
```
    