---
title: "Simulation Information"
author: "Edward Gunning"
date: "2023-08-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Path: -------------------------------------------------------------------
simulation_results_path <- "/Users/edwardgunning/Dropbox/simulation"
```

The simulations were run on the Irish Centre for High-End Computing (ICHEC) cluster. This document provides the `sessionInfo()` from each scenario as well as the number of cores used.

## Baseline Scenario: $N=280$, `prop_missing` $=0.1$, `long_strength` $=1$

```{r}
N_sub_280_prop_missing_0.1_long_strength_1 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_280_prop_missing_0.1_long_strength_1.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_280_prop_missing_0.1_long_strength_1[[1]]$session_info
```

* For this scenario, there were `r N_sub_280_prop_missing_0.1_long_strength_1[["n_cores"]]` cores used.

## $N=280$, `prop_missing` $=0.1$, `long_strength` $=2$

```{r}
N_sub_280_prop_missing_0.1_long_strength_2 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_280_prop_missing_0.1_long_strength_2.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_280_prop_missing_0.1_long_strength_2[[1]]$session_info
```

* For this scenario, there were `r N_sub_280_prop_missing_0.1_long_strength_2[["n_cores"]]` cores used.



## $N=280$, `prop_missing` $=0.1$, `long_strength` $=3$

```{r}
N_sub_280_prop_missing_0.1_long_strength_3 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_280_prop_missing_0.1_long_strength_3.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_280_prop_missing_0.1_long_strength_3[[1]]$session_info
```

* For this scenario, there were `r N_sub_280_prop_missing_0.1_long_strength_3[["n_cores"]]` cores used.


## $N=280$, `prop_missing` $=0.2$, `long_strength` $=1$

```{r}
N_sub_280_prop_missing_0.2_long_strength_1 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_280_prop_missing_0.2_long_strength_1.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_280_prop_missing_0.2_long_strength_1[[1]]$session_info
```

* For this scenario, there were `r N_sub_280_prop_missing_0.1_long_strength_1[["n_cores"]]` cores used.

## $N=280$, `prop_missing` $=0.5$, `long_strength` $=1$

```{r}
N_sub_280_prop_missing_0.5_long_strength_1 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_280_prop_missing_0.5_long_strength_1.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_280_prop_missing_0.5_long_strength_1[[1]]$session_info
```

* For this scenario, there were `r N_sub_280_prop_missing_0.5_long_strength_1[["n_cores"]]` cores used.


## $N=500$, `prop_missing` $=0.1$, `long_strength` $=1$

```{r}
N_sub_500_prop_missing_0.1_long_strength_1 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_500_prop_missing_0.1_long_strength_1.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_500_prop_missing_0.1_long_strength_1[[1]]$session_info
```

* For this scenario, there were `r N_sub_500_prop_missing_0.1_long_strength_1[["n_cores"]]` cores used.

## $N=1000$, `prop_missing` $=0.1$, `long_strength` $=1$

Due to out-of-memory (OOM) errors, this was split into two smaller batches of simulations ($250$ replicates each).

### Part 1

```{r}
N_sub_1000_prop_missing_0.1_long_strength_1 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_1000_prop_missing_0.1_long_strength_1.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_1000_prop_missing_0.1_long_strength_1[[1]]$session_info
```

* For this scenario, there were `r N_sub_1000_prop_missing_0.1_long_strength_1[["n_cores"]]` cores used.


### Part 2

```{r}
N_sub_1000_prop_missing_0.1_long_strength_1_part_2 <- readRDS(
  file.path(
    simulation_results_path,
    "N_sub_1000_prop_missing_0.1_long_strength_part_21.rds"
  )
)
# grab sessionInfo from first replicate:
N_sub_1000_prop_missing_0.1_long_strength_1_part_2[[1]]$session_info
```

* For this scenario, there were `r N_sub_1000_prop_missing_0.1_long_strength_1_part_2[["n_cores"]]` cores used.
